### 2018-05-02 paper/evaluation.tex
a

\paragraph*{PORs creation}
Figures \ref{fig:nodes_per_layer_vs_theta} and \ref{fig:success_rate_vs_t} come from the same data, with 10 experiments per set of settings.
$\theta$, the threshold of the probability that all nodes fail at once (cf. \ref{ssub:building_routes}), takes the following values: $[0.1, 0.01, 0.001, 0.0001]$.
$L$, the number of layers constituting a route, takes the following values: $[3, 5, 7]$.
The time since route establishment goes from 1 to 10 with  unit step.
It is measured in time periods $T$, the interval at which users change the connection state of their devices.
An experiment consisted in $L*5$ users, where we randomly picked pairs of users to compute 20 routes.
Hence, each point in figure~\ref{fig:nodes_per_layer_vs_theta} is the average of 3000 layers size; 
each point in figure~\ref{fig:nodes_per_layer_vs_theta} is the availability rate over 200 routes.

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.7\columnwidth]{figures/nodes_per_layer_vs_theta.pdf}
\caption{\label{fig:nodes_per_layer_vs_theta}Number of nodes per layer of POR as a function of the parameter $\theta$ (the maximal probability that all nodes in a layer fail at once). The number of nodes logarithmically decreases as we relax the $\theta$ constraint.}
\end{figure}

We first measure the influence of the parameter $\theta$ on the number of nodes per layer in figure~\ref{fig:nodes_per_layer_vs_theta}, by displaying average and standard deviation of the number of nodes for $\theta=[10^{-4}, 10^{-3}, 10^{-2}, 10^{-1}]$ (the other experiment parameters are listed in section~\ref{ssub:experimental_parameters}).
As we can see, the number of devices per layer logarithmically decreases as we relax the constraint on the layer's availability.
The mean number of devices per layer lies between 2 and 6.
Still, the number of nodes per layer is very variable: at $\theta=10^{-4}$, values range from 2 to 11, with a standard deviation of 1.44.

\begin{figure}[t]
\includegraphics[width=0.9\columnwidth]{figures/success_rate_vs_t.pdf}
\caption{\label{fig:success_rate_vs_t}Availability rate of routes as a function of the time since the route establishment, for several values of the parameters $\theta$ (the maximal probability that all nodes in a layer fail at once) and $L$ (the number of layers in the route).}
\end{figure}

>>>>

\paragraph*{PORs creation}
Figure \ref{fig:success_rate_vs_t} come from the same data, with 10 experiments per set of settings.
$\theta$, the threshold of the probability that all nodes fail at once (cf. \ref{ssub:building_routes}), takes the following values: $[0.1, 0.01, 0.001, 0.0001]$.
$L$, the number of layers constituting a route, takes the following values: $[3, 5, 7]$.
The time since route establishment goes from 1 to 10 with  unit step.
It is measured in time periods $T$, the interval at which users change the connection state of their devices.
An experiment consisted in $L*5$ users, where we randomly picked pairs of users to compute 20 routes.
Hence, each point on the top of figure~\ref{fig:nodes_per_layer_vs_theta} is the average of 3000 layers size; 
each point on the bottom is the availability rate over 200 routes.

@@

We first measure the influence of the parameter $\theta$ on the number of nodes per layer on the top of figure~\ref{fig:success_rate_vs_t}, by displaying average and standard deviation of the number of nodes for $\theta=[10^{-4}, 10^{-3}, 10^{-2}, 10^{-1}]$ (the other experiment parameters are listed in section~\ref{ssub:experimental_parameters}).
As we can see, the number of devices per layer logarithmically decreases as we relax the constraint on the layer's availability.
The mean number of devices per layer lies between 2 and 6.
Still, the number of nodes per layer is very variable: at $\theta=10^{-4}$, values range from 2 to 11, with a standard deviation of 1.44.

\begin{figure}[t]
\centering
\includegraphics[width=0.7\columnwidth]{figures/nodes_per_layer_vs_theta.pdf}
\vspace{2ex}
\includegraphics[width=0.9\columnwidth]{figures/success_rate_vs_t.pdf}
\caption{\label{fig:success_rate_vs_t}On top: Number of nodes per layer of POR as a function of the parameter $\theta$ (the maximal probability that all nodes in a layer fail at once). The number of nodes logarithmically decreases as we relax the $\theta$ constraint. On bottom: Availability rate of routes as a function of the time since the route establishment, for several values of the parameters $\theta$ (the maximal probability that all nodes in a layer fail at once) and $L$ (the number of layers in the route).}
\end{figure}
